Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-04 doc/manuscript/ESSDmanuscript.Rmd
trying (failing) to make table formatting work

\newpage 
**Table 1: variables with definitions and measurement methods.** Definitions from IPCC Table 1.1. (See Table 1.1 in IPCC guidance). (*Currently adding this as a figure (generated from original draft) because kableExtra doesn't seem to work in this template. Table that we want here is "figures_tables/C_pools.csv"*)

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Table 1"}
knitr::include_graphics("figures_tables/C_pools_fig.png")
```

>>>>

\newpage

**Table 1: variables with definitions and measurement methods.** Definitions from IPCC Table 1.1. (See Table 1.1 in IPCC guidance). (*Currently adding this as a figure (generated from original draft) because kableExtra doesn't seem to work in this template, and I can't quickly get the template format to work. Table that we want here is "figures_tables/C_pools.csv"*)

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Table 1"}
#this is for a two-column figure. for one-column figure, use {r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("figures_tables/C_pools_fig.png")
```

\begin{table*}[t]
\caption{This is a start at table 1 using the template format. }
\begin{tabular}{l c c c r}
\tophline

pool & subpool & definition & major sources of estimate variation & IPCC guidance \\
\middlehline
biomass & aboveground & all biomass of living vegetation, both woody and herbaceous, above the soil & allometry, min dbh & acceptable to exclude understory  \\

\bottomhline
\end{tabular}
\belowtable{I don't know how to adjust so that it doesn't run off the page.}
\end{table*}

### 2021-06-04 doc/manuscript/ESSDmanuscript.tex
trying (failing) to make table formatting work

\textbf{Table 1: variables with definitions and measurement methods.}
Definitions from IPCC Table 1.1. (See Table 1.1 in IPCC guidance).
(\emph{Currently adding this as a figure (generated from original draft)
because kableExtra doesn't seem to work in this template. Table that we
want here is ``figures\_tables/C\_pools.csv''})

@@

>>>>

\textbf{Table 1: variables with definitions and measurement methods.}
Definitions from IPCC Table 1.1. (See Table 1.1 in IPCC guidance).
(\emph{Currently adding this as a figure (generated from original draft)
because kableExtra doesn't seem to work in this template, and I can't
quickly get the template format to work. Table that we want here is
``figures\_tables/C\_pools.csv''})

@@

\begin{table*}[t]
\caption{This is a start at table 1 using the template format. }
\begin{tabular}{l c c c r}
\tophline

pool & subpool & definition & major sources of estimate variation & IPCC guidance \\
\middlehline
biomass & aboveground & all biomass of living vegetation, both woody and herbaceous, above the soil & allometry, min dbh & acceptable to exclude understory  \\

\bottomhline
\end{tabular}
\belowtable{I don't know how to adjust so that it doesn't run off the page.}
\end{table*}
